TODO (re-replication) (student) (cumulative science) (failure to replicate) 

### 2024-02-23 manuscript/manuscript.Rmd
smdification, plot futzing

```{r, fig.cap="TODO"}

#test on just one
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE) 
for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)

orig_scale <- ggplot(for_plotting,aes(x=reorder(name_pretty, point, FUN=max), y,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="effect size on original scale", x="")

smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
  coord_flip(ylim=c(-1.1,1.5))+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
```

@@

```{r, fig.height=6, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")

 ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black", alpha=.5)+
  geom_point(aes(y=d), color="black", position=position_dodge(width=.3), shape=1, alpha=.5)+
     geom_point(size=2.5, position=position_dodge(width=.4))+

  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position="bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_color_manual(values=colors)+
  labs(y="predInts on SMD scale", x="")

>>>>

```{r, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available. Due to the large effect size of a couple studies, large effect studies are shown in a separate panel. "}

#test on just one
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)

big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1) |> select(target_lastauthor_year)
for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)

smd_scale_small <- ggplot(for_plotting_d |> anti_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
 coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
  scale_shape_manual(values=shape)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

smd_scale_big <- ggplot(for_plotting_d |> inner_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
 coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
    scale_shape_manual(values=shape)+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

#smd_scale_big
#smd_scale_small

plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.3,1), nrow=2)
```

@@

```{r, fig.height=6, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
col_code <- c("TRUE"="darkgreen", "FALSE"="black")

big <- predInts_het |> filter(d>1) |> select(target_lastauthor_year)

small_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> anti_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, fill=type, color=d_inside, group=desc(type), shape=type))+
  geom_errorbar(size=.5, width=.25, position=position_dodge(width=.4), alpha=.5)+
  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position="bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_fill_manual(values=colors)+
  scale_shape_manual(values=shape)+
  scale_color_manual(values=col_code)+
  labs(y="predInts on SMD scale", x="")

big_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> inner_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=d_inside, fill=type, group=desc(type), shape=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), alpha=.5)+
  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position="none", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  scale_fill_manual(values=colors)+
  scale_shape_manual(values=shape)+
  scale_color_manual(values=col_code)+
  labs(y="predInts on SMD scale", x="")

plot_grid(big_predInt, small_predInt, nrow=2, rel_heights = c(.3,1))
